conmat: generate synthetic contact matrices for a given age population

### 2024-06-13 paper/paper.Rmd
Improved draft

As an example, let us generate a contact matrix for a local area using POLYMOD data.

Suppose we want to get a contact matrix for a given region in Australia, let's say the city of Perth. We can get that from a helper function, `abs_age_lga`.

@@

We can get a contact matrix made for `perth` using the `extrapolate_polymod` function:

@@

We can plot this with `autoplot`

@@

Conmat was built to predict at four settings: work, school, home, and other. The model is built to predict four separate models, one for each setting.
The model is a poisson generalised additive model (gam), predicting the count of contacts, with an offset of the log of participants. There are six terms to explain six key features of the relationship between ages, and optional terms for attendance at school or work, depending on which setting the model is predicting to.

>>>>

As an example, let us generate a contact matrix for a local area using a model fitted from the POLYMOD data.

Suppose we want to generate a contact matrix for the City of Perth in Australia. We can get the population data for Perth from the helper function `abs_age_lga`:

@@

We can generate a contact matrix for `perth` using the `extrapolate_polymod` function, where the contact matrix is generated using a model fitted from the POLYMOD data.

@@

We can plot the resulting contact matrix with `autoplot`:

@@

Conmat was built to predict at four settings: work, school, home, and other. The model is built to predict four separate models, one for each setting.
The model is a Poisson generalised additive model (GAM), predicting the count of contacts, with an offset of the log of participants. There are six terms to explain six key features of the relationship between ages, and optional terms for attendance at school or work, depending on which setting the model is predicting to.
